\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-07 tex/paper.tex
Added sections to the presentation

\end{description}
\newpage
\section{Model} \label{sec:model}
This section describes how different operations can be expected to effect the data in the system.
The model for this work also shows how the data can only be accessed or modified by
authorized users and how the defined integrity of the data is always kept in the Perius system.

>>>>

\end{description}
\newpage
\section{Model} \label{sec:model}
This section describes how different operations can be expected to effect the data in the system.
The model for this work also shows how the data can only be accessed or modified by
authorized users and how the defined integrity of the data is always kept.
